---
title: "Summary of IC Chemistry Publications"
author: "hjuinj"
date: "2016-08-11"
output: html_document
---

Load packages and establish connection to Mongodb.
```{r warning = FALSE}
library(rmongodb)
library(stringr)
library(ggplot2)

mongo <- mongo.create()
if(mongo.is.connected(mongo) == TRUE) {
    db <- mongo.get.databases(mongo)
    coll <- mongo.get.database.collections(mongo, db)
}
```

The records are obtained from `r length(mongo.distinct(mongo, coll, "from"))` staffs. We can look at the relative proportion of Doctors and Proffesors in the department.

```{r }
df <- data.frame(names = mongo.distinct(mongo, coll, 'from'))
df$isProf <- str_detect(toupper(df$names), "PROFESSOR")
ggplot(df, aes(x = factor(1), fill = isProf) ) + geom_bar()  + coord_polar(theta = "y")+ theme(axis.title.x=element_blank(),        
        axis.text.x=element_blank(),
        axis.title.y=element_blank(),
        axis.text.y=element_blank())

```

---

There are in total `r mongo.count(mongo, coll)` entries. The entries are of the following types:
```{r echo = FALSE}
mongo.distinct(mongo, coll, 'publication-type')
```

We can take a look at how many entries of each publication type are there, note the y-axis is on a log scale:
```{r }
df <- mongo.find.all(mongo, coll, fields = list('publication-type' = 1, '_id' = 0), data.frame = T)
ggplot(df, aes(x = publication.type) ) + geom_bar() + 
    theme(axis.text.x = element_text(angle = 90, hjust = 1)) + scale_y_log10(breaks = c(1,10,100,1000,10000)) 
```

It is most interesting to look at only journal & conference publications, which are the vast majority of entries anyways. There are `r mongo.count(mongo, coll, query=list("$or" = list(list("publication-type" = "JOURNAL ARTICLE"), list("publication-type" = "CONFERENCE PAPER"))))` such entries. 

staffs proffessor or doctor

